---
title: "Ramen Report.Rmd"
author: "Danyu Zhang"
date: "2021/3/18"
output: html_document
params:
  data: NA
---

The dataset used is the Ramen Ratings dataset taken from Kaggle, you can enter the [link](https://www.kaggle.com/residentmario/ramen-ratings) for more details. 

The original dataset consists 7 variables which are the followings: 

- **Review**: The reviewed number of each Ramen

- **Brand**: The brand of the Ranmen

- **Variety**: Details of the the Ramen

- **Style**: The style (type) of the Ramen, e.g. Cup or Pack

- **Stars**: The rating of the Ramen

- **Country**: The original Country of the Ramen

- **Top_ten**: indicates the rating of the Ramen from 1 to 10 for years 2012-2016

We modify the data in order to be more comfortable to analyze it. Here is a example of it. 
```{r}
knitr::kable(
    head(params$data),
    booktabs=TRUE,
    longtable=TRUE,
    caption="caption"
)
```

Boxplot of Ratings according to different different countries: 
```{r}
data %>% plot_ly(y = ~Stars, alpha = 0.1, boxpoints = "suspectedoutliers") %>% 
  add_boxplot(x= ~Country, color="orange")

```

Boxplot of Ratings according to different Ramen types: 
```{r}
data %>% plot_ly(y = ~Stars, alpha = 0.1, boxpoints = "suspectedoutliers") %>% 
  add_boxplot(x= ~Style, color="orange")
```

